formula1

### 2020-03-08 inst/formula1.Rmd
conditions, start work

>>>>

# Conditions

Taking 2017 as an example:

`
venue pole conditions\
AUS Hamilton   dry \
CHN Hamilton   wet \
BHR Bottas     dry \
RUS Vettel     dry \
ESP Hamilton   dry \
MON Raikkonen  dry \
CAN Hamilton   dry \
AZE Hamilton   dry \
AUT Bottas     dry \
GBR Hamilton   dry \
HUN Vettel     dry \
BEL Hamilton   dry \
ITA Hamilon    dry \
SIN Vettel     wet \
MAL Hamilton   dry \
JPN Hamilton   dry \
USA Hamilton   dry \
MEX Vettel     dry \
BRA Bottas     dry \
ABU Bottas     dry \
`
